Soling at the 2000 Summer Olympics

### 2020-08-23 inst/soling.Rmd
fix soling for names

```{r, definef}
rr <- function(H,M){
	for(i in seq_len(nrow(M)-1)){
		for(j in (i+1):ncol(M)){
			if(M[i,j]){
				winner <- i
				loser  <- j
			} else {
				winner <- j
				loser <- i
			}
			H[winner] %<>% inc
			H[c(winner,loser)] %<>% dec
		}
	}
	return(H)
}
```

>>>>

```{r, definef}
rr <- function(H,M){
	for(i in seq_len(nrow(M)-1)){
		for(j in (i+1):ncol(M)){
			if(M[i,j]){
				winner <- rownames(M)[i]
				loser  <- rownames(M)[j]
			} else {
				winner <- rownames(M)[j]
				loser <-  rownames(M)[i]
			}
			H[winner] %<>% inc
			H[c(winner,loser)] %<>% dec
		}
	}
	return(H)
}
```
